---
title: "AssignmentMetaanalysis"
author: "hanwenmiao 436819"
date: "2024-05-27"
output: html_document
---
##Load the packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(meta)
library(metafor)
library(dplyr)
```
##Import the data.
```{r}
setwd("C:/Users/lulut/Desktop/forked/11. Metaanalysis")
data <- read_excel("data/metaanalysis_data.xlsx")
head(data)
```
##Set two groups of variables. The first group - control group.(Mean_boys_play_male and Mean_girls_play_female). Then calculate the effect size and combine the effect.
```{r}
m.control <- metacont(
  n.e = N_boys,
  mean.e = Mean_boys_play_male,
  sd.e = SD_boys_play_male,
  n.c = N_girls,
  mean.c = Mean_girls_play_female,
  sd.c = SD_girls_play_female,
  data = data,
  studlab = Study,
  fixed = TRUE,
  random = TRUE
)
summary(m.control)
##Draw a forest plot
m.control %>% forest(sortvar=TE)
```
## According to the forest plot. we can see that most of them gather around true effect.
## Use metareg to check if methods and quality affect results
```{r}
regression1 <- metareg(m.control, formula = `Parental opinion` + `Representativeness of cases`)
summary(regression1)
```
##Based on the results of this model, the p-value is higher than the 5% significance level. Parental opinion and Representativeness of cases do not have a significant effect on results.
##Use metareg to check if author gender affects results
```{r}
author_gender_reg1 <- metareg(m.control, formula = `Female authors` + `Male authors`)
summary(author_gender_reg1)
```
##According to the result. Female authors and Male authors do not have a significant effect on the model results at the 5% significance level.
##Create a 'contour-enhanced' funnel plot.
```{r}
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(m.control, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```
##The funnel plot shows that most data points are around medium standard errors. And the plot is roughly symmetric, suggesting that there is no publication bias.

##The second group of variables:(Mean_boys_play_female and Mean_girls_play_male) And check the effect size.
```{r}
m.control2 <- metacont(
  n.e = N_boys,
  mean.e = Mean_boys_play_female,
  sd.e = SD_boys_play_female,
  n.c = N_girls,
  mean.c = Mean_girls_play_male,
  sd.c = SD_girls_play_male,
  data = data,
  studlab = data$Study,
  fixed = TRUE,
  random = TRUE
)
summary(m.control2)

##Draw a forest plot
m.control2 %>% forest(sortvar=TE)
```

```{r}
## Use metareg to check if methods and quality affect results. Repeat the previous steps. 
regression2 <- metareg(m.control2, formula = `Parental opinion` + `Representativeness of cases`)
summary(regression2)
```
##Parental opinion is not significant .

```{r}
author_gender_reg2 <- metareg(m.control2, formula = `Female authors` + `Male authors`)
summary(author_gender_reg2)
```
##We can see Authors' genders do not affect results.
```{r}
funnel(m.control2, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```
